%------------------------
% Résumé — "clean" variant (2-page)
% Based on Anubhav Singh's MIT-licensed template (github.com/xprilion),
% filled with Swayam Singh's data; header swapped for a centered name +
% FontAwesome contact row (matching the original design).
%------------------------
\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{\vspace{-6pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule\vspace{-4pt}]

%------ custom commands ------
\newcommand{\resumeItem}[2]{\item\small{\textbf{#1}: #2}\vspace{-1pt}}
\newcommand{\resumeItemPlain}[1]{\item\small{#1}\vspace{-1pt}}
\newcommand{\resumeSubheading}[4]{%
  \vspace{1pt}\item[]
    \begin{tabular*}{0.99\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      {\small #3} & {\small #4} \\
    \end{tabular*}\vspace{-1pt}}
\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}}
\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}, itemsep=3pt, topsep=3pt, parsep=0pt]}
\newcommand{\resumeHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=1.3em, label=$\bullet$, itemsep=1.5pt, topsep=2pt, parsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-3pt}}

\begin{document}

%---------- HEADING (centered name + icon contact row) ----------
\begin{center}
  {\Huge\bfseries Swayam Singh}\\[4pt]
  \small
  \faEnvelope~\href{mailto:singhswayam008@gmail.com}{singhswayam008@gmail.com}
  \hspace{1.2em}
  \faPhone*~+91~9116277756
  \hspace{1.2em}
  \href{https://github.com/SwayamInSync}{\faGithub~GitHub}
  \hspace{1.2em}
  \href{https://www.linkedin.com/in/swayam-singh-406610213/}{\faLinkedin~LinkedIn}
  \hspace{1.2em}
  \href{https://scholar.google.com/citations?user=clLJfm8AAAAJ}{\faGraduationCap~Google Scholar}
\end{center}

%----------- EDUCATION -----------
\section{Education}
\resumeHeadingListStart
  \resumeSubheading
    {\href{https://www.allduniv.ac.in/}{University of Allahabad}}{2020 -- 2024}
    {B.Tech, Computer Science and Engineering}{CGPA: 9.56}
\resumeHeadingListEnd

%----------- EXPERIENCE -----------
\vspace{-2pt}
\section{Experience}
\resumeHeadingListStart
  \resumeSubheading{\href{https://www.microsoft.com/en-us/research/lab/microsoft-research-india/}{Microsoft Research}}{10/2024 -- Present}{Research Fellow}{}
    \resumeItemListStart
      \resumeItemPlain{Developed \& trained the world's first model and training pipeline for End-To-End Autoformalization and verification of programs in Rust}
      \resumeItemPlain{Engineered the mid-training and post-training recipe for model learn formalizing program with formal guarantee, translating natural-language and informal specs into formally verifiable representations.}
      \resumeItemPlain{Developing foundational algorithms that exploit reinforcement-learning gradient-optimization dynamics to improve representation efficiency, stability, and generalization.}
      \resumeItemPlain{Developed an LLM on par with Gemini and GPT-4o for code generation, instruction-following, and reasoning; post-pretraining and online/offline RL.}
      \resumeItemPlain{Developed SeleKT, a supervised fine-tuning method that preserves generalization while significantly improving downstream performance.}
      \resumeItemPlain{Led large-scale training on multi-GPU clusters, optimizing distributed workflows for high-performance code synthesis.}
    \resumeItemListEnd

  \resumeSubheading{\href{https://numpy.org/}{NumPy (numpy-quaddtype)}}{12/2024 -- Present}{Maintainer}{}
    \resumeItemListStart
      \resumeItemPlain{Review, merge, and evaluate core PRs affecting dtype architecture, numerical semantics, and cross-platform behavior.}
      \resumeItemPlain{Maintain core NumPy with a focus on dtype infrastructure, numerical correctness, and long-term maintenance.}
      \resumeItemPlain{Work with contributors across architectures on portability, performance, and ABI concerns.}
    \resumeItemListEnd

  \resumeSubheading{\href{https://quansight.com/}{Quansight}}{07/2024 -- 09/2024}{Open Source Intern -- Numerical Types \& Precision (NumPy OSS)}{}
    \resumeItemListStart
      \resumeItemPlain{Led development of NumPy-QuadDType, a cross-platform 128-bit floating-point system for consistent quad precision beyond platform-dependent long double.}
      \resumeItemPlain{Implemented full dtype ecosystem integration: casting, ufunc dispatch, scalar types, memory model, and serialization.}
      \resumeItemPlain{Built multi-platform distribution and testing infrastructure handling compiler toolchains, SIMD availability, FMA support, and architecture-specific behavior.}
    \resumeItemListEnd

  \resumeSubheading{dataX.ai}{05/2022 -- 10/2022}{Machine Learning Engineer Intern}{}
    \resumeItemListStart
      \resumeItemPlain{Built deep-learning models for vision and language; created an ONNX conversion API with Triton deployment, cutting VM load by 12\%.}
      \resumeItemPlain{Wrote custom CUDA kernels for 3D medical-scan processing, achieving a 2x speedup in segmentation over existing GPU solutions.}
    \resumeItemListEnd

  \resumeSubheading{Scaler (InterviewBit)}{2022}{Data Science Intern}{}
    \resumeItemListStart
      \resumeItemPlain{Built predictive models and data-preprocessing automation, improving user engagement by \textasciitilde25\%.}
    \resumeItemListEnd
\resumeHeadingListEnd

%----------- PUBLICATIONS -----------
\vspace{-2pt}
\section{Publications}
\resumeItemListStart
  \resumeItemPlain{\textbf{\href{https://www.microsoft.com/en-us/research/publication/nextcoder-robust-adaptation-of-code-lms-to-diverse-code-edits/}{NextCoder: Robust Adaptation of Code LMs to Diverse Code Edits}} (ICML 2025; ICLR 2025 DL4Code).\\ \textbf{Swayam Singh}, Tushar Aggarwal, et al. A synthetic-data generation pipeline and SeleKT (Selective Knowledge Transfer), a new fine-tuning algorithm that makes code LLMs robust to diverse, real-world code edits. Our 32B model matches Gemini and beats GPT-4o on harder tasks like aider-polyglot, achieved purely via SFT, with SeleKT substantially reducing catastrophic forgetting compared to other methods.}
  \resumeItemPlain{\textbf{\href{https://arxiv.org/abs/2407.03941}{Narrow Transformer: StarCoder-Based Java-LM For Desktop}} (arXiv:2407.03941, 2024).\\ Kamalkumar Rathinasamy, \ldots, \textbf{Swayam Singh}, et al. A compact, Java-specialized code language model designed to run efficiently on desktop hardware.}
  \newpage
  \resumeItemPlain{\textbf{\href{https://arxiv.org/abs/2308.07124}{OctoPack: Instruction Tuning Code Large Language Models}} (ICLR 2024 Spotlight; NeurIPS 2023 Instruction Workshop).\\ Niklas Muennighoff, \ldots, \textbf{Swayam Singh}, et al. Instruction tuning of code models using natural-language Git commits (CommitPack / CommitPackFT).}
  \resumeItemPlain{\textbf{\href{https://arxiv.org/abs/2305.06161}{StarCoder: May the Source Be With You!}} (TMLR 2023).\\ Raymond Li, \ldots, \textbf{Swayam Singh}, et al.\ (BigCode). A 15.5B-parameter open code LLM trained on 1T tokens of permissively licensed code.}
\resumeItemListEnd

%----------- PROJECTS (flows immediately after publications) -----------
\section{Projects}
\resumeItemListStart
  \resumeItem{\href{https://github.com/SwayamInSync/clothes-virtual-try-on}{Virtual Clothing Assistant} (PyTorch)}{An end-to-end virtual try-on system: ResNet101 and UNet for garment/body segmentation, OpenPose for pose estimation, and a PyTorch VITON pipeline for realistic garment warping. Reaches an SSIM of 0.895 and has 500+ GitHub stars.}
  \resumeItem{\href{https://github.com/SwayamInSync/numpy-quaddtype}{Numpy-QuadDType} (C, C++, Python)}{A cross-platform 128-bit (quadruple-precision) floating-point dtype for NumPy with 100k+ downloads. A portable alternative to long double with full casting, ufunc dispatch, scalar types, and serialization that behaves consistently across compilers and architectures.}
  \resumeItem{Bare-Bones Inference (CUDA, C++)}{A minimal inference stack with engine-grade features such as batching and scheduling, but serving a single fused megakernel instead of a conventional multi-kernel pipeline. Built DeepSeek-V2 (236B)'s block-scaled FP8-quantized, multi-GPU megakernel for NVIDIA B200 (sm\_100) GPUs that fuses all computation and TP/EP communication into one kernel, handling cross-rank exchange via \texttt{multimem} PTX multicast writes (directly writing into peer ranks' memory at once). Achieves 13.11 ms/token decode latency, beating vLLM's optimized serving latency at $B{=}1$ by 2x and eager-mode by ${>}10$x.}
  \resumeItem{\href{https://github.com/SwayamInSync/QBLAS}{QBLAS} (C, C++)}{A high-performance BLAS library for IEEE-754 binary128 (quadruple) precision, implementing optimized linear-algebra kernels that bring quad-precision numerics to workloads unsupported by standard double-precision libraries.}
  \resumeItem{\href{https://github.com/SwayamInSync/cpp-verify}{cpp-verify} (C++, LLVM, SMT)}{Extends C++ with first-class formal-verification constructs (pre/post-conditions and invariants), lowering specifications through an LLVM-based pipeline and discharging the resulting proof obligations to SMT solvers.}
  \resumeItem{\href{https://github.com/swayamInSync/mira}{MIRA -- Multimodal Image Reconstruction with Attention} (PyTorch)}{A transformer-based architecture for single-view text/image-to-3D reconstruction using ViT encoders and triplane decoders with cross-attention. Generates 3D mesh and video in under 10s on an A100, with SDXL-integrated diffusion for end-to-end scene synthesis.}
\resumeItemListEnd

%----------- HONORS & AWARDS -----------
\vspace{-2pt}
\section{Honors and Awards}
\resumeItemListStart
  \resumeItemPlain{\textbf{2024} --- \textbf{Kaggle Competition Expert}: Bronze medal (top 7\%) in the UBC-OCEAN competition; top 3\% in the \textit{30 Days of ML} challenge.}
  \resumeItemPlain{\textbf{2024} --- Invited to \textbf{Google Research Week}, Google Research's gathering of AI researchers (keynote by Jeff Dean; sessions on differential privacy, responsible AI, and more).}
  \resumeItemPlain{\textbf{2024} --- \textbf{OctoPack} accepted as a \textbf{Spotlight (top 5\%)} at ICLR 2024.}
  \resumeItemPlain{\textbf{2023} --- Selected for the \textbf{Amazon ML Summer School 2023}.}
  \resumeItemPlain{\textbf{2023} --- \textbf{Clothes Virtual Try-On} crossed 500+ GitHub stars.}
\resumeItemListEnd

%----------- INVITED TALKS -----------
\vspace{-2pt}
\section{Invited Talks}
\resumeItemListStart
  \resumeItemPlain{\textbf{MAMBA: Zero to Hero}, invited talk on State Space Models at Cohere for AI.}
  \resumeItemPlain{\textbf{Provably-Correct Code and Efficient Sparse Training of LLMs}, internal research talk at Microsoft Research.}
  \resumeItemPlain{\textbf{Foundations of Machine Learning}, a GDG On-Campus session on the ML landscape, tooling ecosystem, and emerging directions.}
  \resumeItemPlain{\textbf{From Deep Learning to Large Language Models}, a talk on the foundations of modern AI: deep learning, generative models, and LLMs.}
\resumeItemListEnd

%----------- SKILLS (at the end) -----------
\vspace{-2pt}
\section{Skills Summary}
\resumeItemListStart
  \resumeItem{Languages}{C, C++, CUDA, CuTeDSL, Python}
  \resumeItem{ML \& Training}{LLM post-training, reinforcement learning (online/offline RL), supervised fine-tuning, multi-GPU distributed training, code-generation models}
  \resumeItem{Systems \& GPU}{CUDA kernels and megakernels, high-performance numerical computing, IEEE-754 quad precision, SIMD/FMA, performance optimization}
  \resumeItem{Tools \& Frameworks}{PyTorch, NumPy (C-API internals), LLVM, SMT solvers}
  \resumeItem{Open Source}{Core NumPy maintenance, cross-platform C-extension packaging, code review}
\resumeItemListEnd

\end{document}
